### 2022-12-14 code/1_exclusions/1_exclusionsCN.Rmd
setting up cogsci paper

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

df.resp_M <- df.resp_M %>%
  filter(subject %in% df.ppts_att_M$subject) 
```

```{r exclusion M, include = F, warning = F}
#non-native speaker
split_responses_demog <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

NATIVE_LANG = 2
get_native_lang <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
    {warnings("cannot find native language answer")}
  else
    {return (responses[NATIVE_LANG])}
})

df.ppts_non_native_lang_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language") %>%
  mutate(native_speaker = get_native_lang(responses)) %>%
  filter(native_speaker == "不是")

ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #2
percent_dropped = length(ppts_non_native_lang_M) / length(unique(df.resp_M$subject))
percent_dropped #0.01398601

#fluent in English
SPEAKER = 2
SPEAKING = 23
UNDERSTANDING = 46

get_speaker <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKER])
})

get_fluency_speaking <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKING])
})

get_fluency_understanding <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[UNDERSTANDING])
})

df.lang_en_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_en") %>%
  mutate(en_speaker = get_speaker(responses))

df.lang_en_fluency_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_en_fluency") %>%
  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_en_M <- full_join(df.lang_en_M, 
                          df.lang_en_fluency_M, 
                          by = "subject") %>%
  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
  filter(en_speaker == "能",
         en_fluency_sp > 4, 
         en_fluency_ud > 4)

ppts_en_speaker_M = unique(df.lang_en_M$subject) #50
percent_dropped = length(ppts_en_speaker_M) / length(unique(df.resp_M$subject))
percent_dropped #0.3496503 # will not use this criterion

df.lang_vi_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_vi") %>%
  mutate(vi_speaker = get_speaker(responses))

df.lang_vi_fluency_M <- df.resp_M %>%
  filter(variable_type == "demog_conditional_language_vi_fluency") %>%
  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_vi_M <- full_join(df.lang_vi_M, 
                          df.lang_vi_fluency_M, 
                          by = "subject") %>%
  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
  filter(vi_speaker == "能",
         vi_fluency_sp > 4, 
         vi_fluency_ud > 4)

ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #50
percent_dropped = length(ppts_vi_speaker_M) / length(unique(df.resp_M$subject))
percent_dropped #0

#have lived outside the sample country for more than 2 years
#have travelled extensively (more than 6 international experiences of 2 days or longer) 
YEARSABROAD = 2
OVERSEAEXP = 4

get_lived_abroad <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[YEARSABROAD])
})

get_oversea_exp <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[OVERSEAEXP])
})

df.abroad_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_oversea_experience") %>%
  mutate(lived_abroad = get_lived_abroad(responses)) %>%
  mutate(oversea_exp = get_oversea_exp(responses))

df.lived_abroad_M <- df.abroad_M %>%
  filter(lived_abroad == "是")

ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #23
percent_dropped = length(ppts_lived_abroad_M) / length(unique(df.resp_M$subject))
percent_dropped # 0.1608392

df.oversea_exp_M <- df.abroad_M %>%
  filter(oversea_exp == "六段或更多国际经历")

ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #0
percent_dropped = length(ppts_oversea_exp_M) / length(unique(df.resp_M$subject))
percent_dropped #0

df.resp_M <- df.resp_M %>%
  filter(!(subject %in% ppts_non_native_lang_M),
         !(subject %in% ppts_lived_abroad_M),
         !(subject %in% ppts_vi_speaker_M),
         !(subject %in% ppts_oversea_exp_M),)

length(unique(df.resp_M$subject)) 
```

```{r}
write.csv(df.resp_M, "../../data/dataCN_excl.csv")
```

>>>>

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

df.resp_M <- df.resp_M %>%
  filter(subject %in% df.ppts_att_M$subject)

ppts_resp_M <- unique(df.resp_M$subject)
```

```{r}
df.demog <- read.csv("../../data/responding/data_demog.csv") %>%
  select(-X) %>%
  filter(country == "CN")
```

```{r exclusion E, include = F, warning = F}
#non-native speaker
df.ppts_non_native_lang_M <- df.demog %>%
  filter(demog_question == "firstlanguage" & demog_response == "不是")

ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #3
percent_dropped = length(intersect(ppts_non_native_lang_M, ppts_resp_M)) / length(ppts_resp_M)
percent_dropped #0.01086

#fluent in Vietnamese & Mandarin
df.lang_sp_vi_M <- df.demog %>%
  filter(demog_question == "lang_sp_vi" & demog_response > 4)

df.lang_ud_vi_M <- df.demog %>%
  filter(demog_question == "lang_ud_vi" & demog_response > 4)

df.lang_vi_M <- inner_join(df.lang_sp_vi_M, df.lang_ud_vi_M, by = 'subject')

ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #1
percent_dropped = length(intersect(ppts_vi_speaker_M, ppts_resp_M)) / length(ppts_resp_M)
percent_dropped #0

df.lang_sp_en_M <- df.demog %>%
  filter(demog_question == "lang_sp_en" & demog_response > 4)

df.lang_ud_en_M <- df.demog %>%
  filter(demog_question == "lang_ud_en" & demog_response > 4)

df.lang_en_M <- inner_join(df.lang_sp_en_M, df.lang_ud_en_M, by = 'subject')

ppts_en_speaker_M = unique(df.lang_en_M$subject) #74
percent_dropped = length(intersect(ppts_en_speaker_M, ppts_resp_M)) / length(ppts_resp_M)
percent_dropped #0.375 # do not use this criterion

#have lived outside the sample country for more than 2 years
df.lived_abroad_M <- df.demog %>%
  filter(demog_question == "abroadexp" & demog_response == "是")

ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #40
percent_dropped = length(intersect(ppts_lived_abroad_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
percent_dropped #0.163043

#have travelled extensively (more than 6 international experiences of 2 days or longer)
df.oversea_exp_M <- df.demog %>%
  filter(demog_question == "overseaexpnum" & demog_response == "六段或更多国际经历")

ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #12
percent_dropped = length(intersect(ppts_oversea_exp_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
percent_dropped #0.0434782

df.resp_M <- df.resp_M %>%
  filter(!(subject %in% ppts_non_native_lang_M),
         !(subject %in% ppts_vi_speaker_M), 
         !(subject %in% ppts_lived_abroad_M), 
         !(subject %in% ppts_oversea_exp_M))

length(unique(df.resp_M$subject)) #149
```

```{r}
write.csv(df.resp_M, "../../data/responding/dataCN_excl.csv")
```

### 2022-12-14 code/1_exclusions/1_exclusionsUS.Rmd
setting up cogsci paper

df.ppts_att_E <- df.resp_E %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Choose ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

df.resp_E <- df.resp_E %>%
  filter(subject %in% df.ppts_att_E$subject) 
```

```{r exclusion E, include = F, warning = F}
#non-native speaker
split_responses_demog <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

NATIVE_LANG = 2
get_native_lang <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
    {warnings("cannot find native language answer")}
  else
    {return (responses[NATIVE_LANG])}
})

df.ppts_non_native_lang_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language") %>%
  mutate(native_speaker = get_native_lang(responses)) %>%
  filter(native_speaker == "No")

ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#18
percent_dropped = length(ppts_non_native_lang_E) / length(unique(df.resp_E$subject))
percent_dropped #0.1034482775

#fluent in Vietnamese & Mandarin
SPEAKER = 2
SPEAKING = 23
UNDERSTANDING = 46

get_speaker <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKER])
})

get_fluency_speaking <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKING])
})

get_fluency_understanding <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[UNDERSTANDING])
})

df.lang_vi_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_vi") %>%
  mutate(vi_speaker = get_speaker(responses))

df.lang_vi_fluency_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_vn_fluency") %>%
  mutate(vi_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(vi_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_vi_E <- full_join(df.lang_vi_E, 
                          df.lang_vi_fluency_E, 
                          by = "subject") %>%
  select(subject, vi_speaker, vi_fluency_sp, vi_fluency_ud) %>%
  filter(vi_speaker == "Yes",
         vi_fluency_sp > 4, 
         vi_fluency_ud > 4)

ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #4
percent_dropped = length(ppts_vi_speaker_E) / length(unique(df.resp_E$subject))
percent_dropped #0.02298851

df.lang_zh_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_cn") %>%
  mutate(zh_speaker = get_speaker(responses))

df.lang_zh_fluency_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_zh_E <- full_join(df.lang_zh_E, 
                          df.lang_zh_fluency_E, 
                          by = "subject") %>%
  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
  filter(zh_speaker == "Yes",
         zh_fluency_sp > 4, 
         zh_fluency_ud > 4)

ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
percent_dropped = length(ppts_zh_speaker_E) / length(unique(df.resp_E$subject))
percent_dropped #0.1742424

#have lived outside the sample country for more than 2 years
#have travelled extensively (more than 6 international experiences of 2 days or longer) 
YEARSABROAD = 2
OVERSEAEXP = 4

get_lived_abroad <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[YEARSABROAD])
})

get_oversea_exp <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[OVERSEAEXP])
})

df.abroad_E <- df.resp_E %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_oversea_experience") %>%
  mutate(lived_abroad = get_lived_abroad(responses)) %>%
  mutate(oversea_exp = get_oversea_exp(responses))

df.lived_abroad_E <- df.abroad_E %>%
  filter(lived_abroad == "Yes")

ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #29
percent_dropped = length(ppts_lived_abroad_E) / length(unique(df.resp_E$subject))
percent_dropped #0.1666667

df.oversea_exp_E <- df.abroad_E %>%
  filter(oversea_exp == "Six or more experiences")

ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #77
percent_dropped = length(ppts_oversea_exp_E) / length(unique(df.resp_E$subject))
percent_dropped #0.44 # will not use this criterion

@@

length(unique(df.resp_E$subject)) #132
```

```{r}
write.csv(df.resp_E, "../../data/dataUS_excl.csv")
```

>>>>

df.ppts_att_E <- df.resp_E %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Choose ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

df.resp_E <- df.resp_E %>%
  filter(subject %in% df.ppts_att_E$subject)

ppts_resp_E <- unique(df.resp_E$subject)
```

```{r}
df.demog <- read.csv("../../data/responding/data_demog.csv") %>%
  select(-X) %>%
  filter(country == "US")
```

```{r exclusion E, include = F, warning = F}
#non-native speaker
df.ppts_non_native_lang_E <- df.demog %>%
  filter(demog_question == "firstlanguage" & demog_response == "No")

ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#20
percent_dropped = length(intersect(ppts_non_native_lang_E, ppts_resp_E)) / length(ppts_resp_E)
percent_dropped #0.104166

#fluent in Vietnamese & Mandarin
df.lang_sp_vi_E <- df.demog %>%
  filter(demog_question == "lang_sp_vi" & demog_response > 4)

df.lang_ud_vi_E <- df.demog %>%
  filter(demog_question == "lang_ud_vi" & demog_response > 4)

df.lang_vi_E <- inner_join(df.lang_sp_vi_E, df.lang_ud_vi_E, by = 'subject')

ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #2
percent_dropped = length(intersect(ppts_vi_speaker_E, ppts_resp_E)) / length(ppts_resp_E)
percent_dropped #0.01041666

df.lang_sp_zh_E <- df.demog %>%
  filter(demog_question == "lang_sp_zh" & demog_response > 4)

df.lang_ud_zh_E <- df.demog %>%
  filter(demog_question == "lang_ud_zh" & demog_response > 4)

df.lang_zh_E <- inner_join(df.lang_sp_zh_E, df.lang_ud_zh_E, by = 'subject')

ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
percent_dropped = length(intersect(ppts_zh_speaker_E, ppts_resp_E)) / length(ppts_resp_E)
percent_dropped #0.15104

#have lived outside the sample country for more than 2 years
df.lived_abroad_E <- df.demog %>%
  filter(demog_question == "abroadexp" & demog_response == "Yes")

ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #36
percent_dropped = length(intersect(ppts_lived_abroad_E, ppts_resp_E)) / length(unique(df.resp_E$subject))
percent_dropped #0.171875

#have travelled extensively (more than 6 international experiences of 2 days or longer)
df.oversea_exp_E <- df.demog %>%
  filter(demog_question == "overseaexpnum" & demog_response == "Six or more experiences")

ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #95
percent_dropped = length(intersect(ppts_oversea_exp_E, ppts_resp_E)) / length(unique(df.resp_E$subject))
percent_dropped #0.4739 # will not use this criterion

@@

length(unique(df.resp_E$subject)) #124
```

```{r}
write.csv(df.resp_E, "../../data/responding/dataUS_excl.csv")
```

### 2022-12-14 code/1_exclusions/1_exclusionsVN.Rmd
added a lot of analysis. prepared to move to coglink_cogsci
setting up cogsci paper

df.ppts_att_V <- df.resp_V %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

df.resp_V <- df.resp_V %>%
  filter(subject %in% df.ppts_att_V$subject) #73
```

```{r exclusion V, include = F}
#non-native speaker
split_responses_demog <- function(responses) {
  responses <- as.character(responses)
  response_list <- unlist(strsplit(responses, ',|:'))
  response_list <- response_list[seq(1, length(response_list))]
  response_list <- gsub("}", "", response_list)
  response_list <- gsub("\"", "", response_list)
  return(response_list)
}

NATIVE_LANG = 2
get_native_lang <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  if(responses[NATIVE_LANG-1] != "{firstlanguage") 
    {warnings("cannot find native language answer")}
  else
    {return (responses[NATIVE_LANG])}
})

df.ppts_non_native_lang_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language") %>%
  mutate(native_speaker = get_native_lang(responses)) %>%
  filter(native_speaker == "Không")

ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)
percent_dropped = length(ppts_non_native_lang_V) / length(unique(df.resp_V$subject))
percent_dropped #0

#fluent in English
SPEAKER = 2
SPEAKING = 23
UNDERSTANDING = 46

get_speaker <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKER])
})

get_fluency_speaking <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[SPEAKING])
})

get_fluency_understanding <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[UNDERSTANDING])
})

df.lang_en_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_en") %>%
  mutate(en_speaker = get_speaker(responses))

df.lang_en_fluency_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_en_fluency") %>%
  mutate(en_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(en_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_en_V <- full_join(df.lang_en_V, 
                          df.lang_en_fluency_V, 
                          by = "subject") %>%
  select(subject, en_speaker, en_fluency_sp, en_fluency_ud) %>%
  filter(en_speaker == "Có",
         en_fluency_sp > 4, 
         en_fluency_ud > 4)

ppts_en_speaker_V = unique(df.lang_en_V$subject) #4
percent_dropped = length(ppts_en_speaker_V) / length(unique(df.resp_V$subject))
percent_dropped #0.6986301 # do not use this criterion

df.lang_zh_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language_cn") %>%
  mutate(zh_speaker = get_speaker(responses))

df.lang_zh_fluency_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_conditional_language_cn_fluency") %>%
  mutate(zh_fluency_sp = as.numeric(get_fluency_speaking(responses))) %>%
  mutate(zh_fluency_ud = as.numeric(get_fluency_understanding(responses)))

df.lang_zh_V <- full_join(df.lang_zh_V, 
                          df.lang_zh_fluency_V, 
                          by = "subject") %>%
  select(subject, zh_speaker, zh_fluency_sp, zh_fluency_ud) %>%
  filter(zh_speaker == "Có",
         zh_fluency_sp > 4, 
         zh_fluency_ud > 4)

ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #4
percent_dropped = length(ppts_zh_speaker_V) / length(unique(df.resp_V$subject))
percent_dropped #0.06557377

#have lived outside the sample country for more than 2 years
#have travelled extensively (more than 6 international experiences of 2 days or longer) 
YEARSABROAD = 2
OVERSEAEXP = 4

get_lived_abroad <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[YEARSABROAD])
})

get_oversea_exp <- Vectorize(function(responses) {
  responses <- split_responses_demog(responses)
  return (responses[OVERSEAEXP])
})

df.abroad_V <- df.resp_V %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_oversea_experience") %>%
  mutate(lived_abroad = get_lived_abroad(responses)) %>%
  mutate(oversea_exp = get_oversea_exp(responses))

df.lived_abroad_V <- df.abroad_V %>%
  filter(lived_abroad == "Có")

ppts_lived_abroad_V = unique(df.lived_abroad_V$subject)
percent_dropped = length(ppts_lived_abroad_V) / length(unique(df.resp_V$subject))
percent_dropped #0.1369863

df.oversea_exp_V <- df.abroad_V %>%
  filter(oversea_exp == "6 lần trở lên")

ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #77
percent_dropped = length(ppts_oversea_exp_V) / length(unique(df.resp_V$subject))
percent_dropped #0.1506849

df.resp_V <- df.resp_V %>%
  filter(!(subject %in% ppts_non_native_lang_V),
         !(subject %in% ppts_oversea_exp_V), 
         !(subject %in% ppts_zh_speaker_V),
         !(subject %in% ppts_lived_abroad_V))

length(unique(df.resp_V$subject)) 
```

```{r}
write.csv(df.resp_V, "../../data/dataVN_excl.csv")
```

>>>>

df.ppts_att_V <- df.resp_V %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

df.resp_V <- df.resp_V %>%
  filter(subject %in% df.ppts_att_V$subject) #73

ppts_resp_V <- unique(df.resp_V$subject) #137
```

```{r}
df.demog <- read.csv("../../data/responding/data_demog.csv") %>%
  select(-X) %>%
  filter(country == "VN")
```

```{r exclusion E, include = F, warning = F}
#non-native speaker
df.ppts_non_native_lang_V <- df.demog %>%
  filter(demog_question == "firstlanguage" & demog_response == "Không")

ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)#2
percent_dropped = length(intersect(ppts_non_native_lang_V, ppts_resp_V)) / length(ppts_resp_V)
percent_dropped #0

#fluent in Vietnamese & Mandarin
df.lang_sp_en_V <- df.demog %>%
  filter(demog_question == "lang_sp_en" & demog_response > 4)

df.lang_ud_en_V <- df.demog %>%
  filter(demog_question == "lang_ud_en" & demog_response > 4)

df.lang_en_V <- inner_join(df.lang_sp_en_V, df.lang_ud_en_V, by = 'subject')

ppts_en_speaker_V = unique(df.lang_en_V$subject) #119
percent_dropped = length(intersect(ppts_en_speaker_V, ppts_resp_V)) / length(ppts_resp_V)
percent_dropped #0.6277 # do not use this criterion

df.lang_sp_zh_V <- df.demog %>%
  filter(demog_question == "lang_sp_zh" & demog_response > 4)

df.lang_ud_zh_V <- df.demog %>%
  filter(demog_question == "lang_ud_zh" & demog_response > 4)

df.lang_zh_V <- inner_join(df.lang_sp_zh_V, df.lang_ud_zh_V, by = 'subject')

ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #9
percent_dropped = length(intersect(ppts_zh_speaker_V, ppts_resp_V)) / length(ppts_resp_V)
percent_dropped #0.05839416

#have lived outside the sample country for more than 2 years
df.lived_abroad_V <- df.demog %>%
  filter(demog_question == "abroadexp" & demog_response == "Có")

ppts_lived_abroad_V = unique(df.lived_abroad_V$subject) #18
percent_dropped = length(intersect(ppts_lived_abroad_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
percent_dropped #0.05839416

#have travelled extensively (more than 6 international experiences of 2 days or longer)
df.oversea_exp_V <- df.demog %>%
  filter(demog_question == "overseaexpnum" & demog_response == "Six or more experiences")

ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #95
percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
percent_dropped #0.4739 # will not use this criterion

df.resp_V <- df.resp_V %>%
  filter(!(subject %in% ppts_non_native_lang_V),
         !(subject %in% ppts_vi_speaker_V), 
         !(subject %in% ppts_zh_speaker_V),
         !(subject %in% ppts_lived_abroad_V))

length(unique(df.resp_V$subject)) #124
```

```{r}
write.csv(df.resp_V, "../../data/responding/dataVN_excl.csv")
```
